Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-18 rebuttal.tex

\item \emph{``software systems for the analysis of large volumes of dynamic, distributed, and data intensive have received relatively less so'' [data intensive $\rightarrow$ frequently accessed data?]}

\textbf{Response:} We think this is actually referring to the summary, where we had ``software systems for the analysis of large volumes of dynamic, distributed, and data intensive have received relatively less.''  This was missing the word applications in the midst of the sentence, which made it confusing. ``Less'' referred to less attention, so ``attention has also been added to make this more clear.'' The sentence is now ``software systems for the analysis of large volumes of dynamic, distributed, and data intensive applications have received relatively less attention.''

\item \emph{``Occasionally data are often naturally distributed and have to be processed near their source, and sometimes data that are localized have to be distributed in order to be processed, either for reasons of performance or for collaborative analytics.'' There are 2 dimensions being described here: 1. data can be created in a set of distributed locations or it can be created in 1 place. 2. data can be processed in 1 place, or it can be processed in distributed locations. The 2 dimensions are orthogonal, and all 4 possibilities occur in real applications. However, the above sentence only captures 2 of the 4 quadrants of the space.}

\textbf{Response:} We've reworked the first paragraph of Section 1 to address this.

@@

\item \emph{``In this paper, we use locally distributed to indicate that data/compute resides on multiple nodes within one data center. Geographically distributed describes the distribution of data and/or compute across multiple data centers'' Given the above, I think it would be better in this definition to also separate out data creation location from compute location. Intro: Define precisely what is meant by ``dynamic,'' here as it is key to the paper but isn't well defined in Section 1 (see recommendation above to fix this by moving definitions from Section 3).}

\textbf{Response:}

\katznote{attention needed here re distributed and dynamic part of comment}

\katznote{Neil will add a sentence in the start of Section 2 to say how we are using distributed and how we are using dynamic, in the text that refers to Figure 1.}

In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.  We have also
added a longer description of each section at this same place.  Also, see our response to point 10 below.

@@

\item \emph{``We also introduce the concept of an `infrastructure' application as a collection of infrastructure components that are packaged so that they can be used by many applications in defined ways'' See earlier comments. This doesn't sound to me like an application, but instead a set of infrastructure support services (``components'') packaged from more basic services/components. Again, the use of application with 2 different meanings in this same sentence doesn't help the read to understand what is meant here.}

  \textbf{Response:} We have: (i) provided background discussion about the overloading of the term application, (ii) expanded and clarified the discussion of traditional and infrastructural applications.

\item \emph{4.1 -- 4.3 I found these definitions very helpful, but would again recommend that they come before the survey of specific applications so that these terms can be used, and understood by the reader, within the survey.}

  \textbf{Response:} 
The definitions are provided in the manner they are since they are derived from the applications.  We have clarified this in Section 1.2.  \katznote{Omer, add more here?}

### 2016-08-18 rebuttal.tex

\item \emph{``We also introduce the concept of an `infrastructure' application as a collection of infrastructure components that are packaged so that they can be used by many applications in defined ways'' See earlier comments. This doesn't sound to me like an application, but instead a set of infrastructure support services (``components'') packaged from more basic services/components. Again, the use of application with 2 different meanings in this same sentence doesn't help the read to understand what is meant here.}

  \textbf{Response:} We have: (i) provided background discussion about the overloading of the term application, (ii) expanded and clarified the discussion of traditional and infrastructural applications.

\item \emph{4.1 -- 4.3 I found these definitions very helpful, but would again recommend that they come before the survey of specific applications so that these terms can be used, and understood by the reader, within the survey.}

  \textbf{Response:}
There are a number of possible definitions related to terms used in sections 4.1--4.3 in the computer science literature. Our intention in this work was to derive what these mean based on the application survey we carried out. The definitions are therefore provided in the manner they are since they are derived from the applications provided in Section 2.  We have clarified this in Section 1.2 to provide greater guidance to a reader, justifying the order of the sections.   \katznote{Omer, add more here?}

### 2016-08-18 rebuttal.tex

\item \emph{``We also introduce the concept of an `infrastructure' application as a collection of infrastructure components that are packaged so that they can be used by many applications in defined ways'' See earlier comments. This doesn't sound to me like an application, but instead a set of infrastructure support services (``components'') packaged from more basic services/components. Again, the use of application with 2 different meanings in this same sentence doesn't help the read to understand what is meant here.}

  \textbf{Response:} We have: (i) provided background discussion about the overloading of the term application, (ii) expanded and clarified the discussion of traditional and infrastructural applications.

\item \emph{4.1 -- 4.3 I found these definitions very helpful, but would again recommend that they come before the survey of specific applications so that these terms can be used, and understood by the reader, within the survey.}

  \textbf{Response:}
There are a number of possible definitions related to terms used in Sections 4.1--4.3 in the computer science literature. Our intention in this work was to derive what these mean based on the application survey we carried out. The definitions are therefore provided in Section 3 they are since they are derived from the applications provided in Section 2.  We have clarified this in Section 1.2 to provide greater guidance to a reader, justifying the order of the sections.

### 2016-08-18 rebuttal.tex

\item \emph{``software systems for the analysis of large volumes of dynamic, distributed, and data intensive have received relatively less so'' [data intensive $\rightarrow$ frequently accessed data?]}

\textbf{Response:} We think this is actually referring to the summary, where we had ``software systems for the analysis of large volumes of dynamic, distributed, and data intensive have received relatively less.''  This was missing the word applications in the midst of the sentence, which made it confusing. ``Less'' referred to less attention, so ``attention has also been added to make this more clear.'' The sentence is now ``software systems for the analysis of large volumes of dynamic, distributed, and data intensive applications have received relatively less attention.''

\item \emph{``Occasionally data are often naturally distributed and have to be processed near their source, and sometimes data that are localized have to be distributed in order to be processed, either for reasons of performance or for collaborative analytics.'' There are 2 dimensions being described here: 1. data can be created in a set of distributed locations or it can be created in 1 place. 2. data can be processed in 1 place, or it can be processed in distributed locations. The 2 dimensions are orthogonal, and all 4 possibilities occur in real applications. However, the above sentence only captures 2 of the 4 quadrants of the space.}

\textbf{Response:} We've reworded the first paragraph of Section 1 to address this.

@@

\item \emph{``In this paper, we use locally distributed to indicate that data/compute resides on multiple nodes within one data center. Geographically distributed describes the distribution of data and/or compute across multiple data centers'' Given the above, I think it would be better in this definition to also separate out data creation location from compute location. Intro: Define precisely what is meant by ``dynamic,'' here as it is key to the paper but isn't well defined in Section 1 (see recommendation above to fix this by moving definitions from Section 3).}

\textbf{Response:} \katznote{attention needed here}

\nchnote{Partial response:} We have added a summary description of what we mean by distributed and dynamic at the start of Section 2 to reflect the fact that definition of the terminology arose and was refined by the discussions at the workshops, and the analysis of the application scenarios presented.

\katznote{partial response:} In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.  We have also
added a longer description of each section at this same place.

### 2016-08-18 3dpas_intro.tex
Added definitions to address Point 4

The discussions in the workshops and our analysis of the applications
led us to examine the use of data in different parts of the
applications, where we found some common patterns
across applications.  For example, applications that involve
streaming data collect data from sensors, transform and
filter the data, store the results, and then later process (analyze)
the stored results.  In general, we think that all of the applications
we have studied can be mapped to a set of stages or phases.  This is
illustrated in \figurename~\ref{fig:figures_application-stages}.

>>>>

The discussions in the workshops and our analysis of the applications
led us to examine the use of data in different parts of the
applications, 
and informed the terminology we use in the rest of the paper.
We have split the presentation of information on each scenario into three aspects: 
{\em big data aspects}, concerned with the number and volume of data; 
{\em distributed aspects}, concerned with the way data generation, storage and processing are separated; and 
{\em dynamic aspects}, concerned with the spatio-temporal variability of the data or application.
Doing this has enabled us to identify some common patterns
across applications.  For example, applications that involve
streaming data collect data from sensors, transform and
filter the data, store the results, and then later process (analyze)
the stored results.  In general, we think that all of the applications
we have studied can be mapped to a set of stages or phases.  This is
illustrated in \figurename~\ref{fig:figures_application-stages}.
